%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{natbib}
\usepackage{bibentry}
\nobibliography*

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.1\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\name{Andreas Prodromou} % Your name
\address{One Miramar St \\ San Diego 92092} % Your address
\address{(858)~$\cdot$~263~$\cdot$~5813} % Your phone number
\address{prodromou.andreas@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D., Computer Science} \hfill {\bf June 2013 -- Present} \\
\em Department of Computer Science and Engineering \\
\em University of California, San Diego 

{\bf M.Sc., Computer Engineering} \hfill {\bf 2011 -- 2013} \\
\em Department of Electrical and Computer Engineering \\
\em University of Cyprus 

{\bf B.Sc., Computer Engineering} \hfill {\bf 2007 -- 2011} \\
\em Department of Electrical and Computer Engineering \\
\em University of Cyprus 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Advanced Micro Devices (AMD)}{June 2015 -- Sept. 2015}{Co-op Intern}{Austin, TX}
	\item Implemented a dynamic memory management mechanism for hybrid memory configurations.
	\item Focused mainly on the mechanism's scalability to very large memory capacities.
	\item Utilized novel algorithms and clustered micro-architecture to maintain scalability.
	\item Implemented from scratch in cycle-accurate simulator and compared against state-of-the-art proposals.
\end{rSubsection}

\begin{rSubsection}{University of California San Diego, CSE Department}{August 2013 -- Present}{Graduate Student Researcher}{San Diego, CA}
	\item Exploring the capabilities of dynamic dead code elimination.
	\item Evaluating memory controller scheduling policies under emerging technological trends.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Cyprus, CS Department}{June 2011 -- June 2013}{Special Scientist}{Nicosia, Cyprus}
	\item Part of Eurocloud FP7 Project (http://www.eurocloudserver.com/) -- European research and development program for building a 3D server-on-chip concept integrating low power cores.
	\item Research in Network-on-Chip Reliability.
	\item Designed and evaluated circuit-level modules to detect hardware faults. (Published in MICRO'45 conference)
	\item Participated in assessing the impact design changes have at the datacenter level.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Cyprus, ECE Department}{June 2010 -- September 2010}{Special Scientist}{Nicosia, Cyprus}
	\item Implementation of a parameterized cycle-accurate Network-on-Chip simulator as part of a Full-System simulator (extensive programming and simulations)
	\item Later awarded as Best Senior Design Project
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{KIOS Research Center for Intelligent Systems \& Networks}{June 2009 -- September 2009}{Undergraduate Research Scientist}{Nicosia, Cyprus}
	\item Studied the infrastructure of a Network-on-Chip module
	\item Implemented and assessed routing algorithms for such networks
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}

Memory scheduling policies, dynamic dead code elimination, multicore architectures, 3D microprocessor design, Network-on-Chip architectures. \\

\end{rSection}

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming \& Scripting & C, C++, Java, VHDL, Haskell, Javascript, Perl, Python \\
Debugging & GDB \\
Simulators & Gem5 \& Simics full-system simulators, Garnet NoC simulator, QEMU \\
Architectural Analysis & SPEC \& PARSEC benchmarks, Pin, Simpoint \\
Version Control & Git, SVN \\
Languages & Greek, English\\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\begin{tabular}{L!{\VRule}R}
2012 & NoCAlert: An on-line and real-time fault detection mechanism for network-on-chip architectures, \textbf{A. Prodromou}, A.Panteli, C. Nicopoulos and Y. Sazeides\\[5pt]
2011 & Thermal characterization of cloud workloads on a power-efficient server-on-chip, D. Milojevic, S. Idgunji, D. Jevdjic, E. Ozer, P. Lotfi-Kamran, A. Panteli, \textbf{A. Prodromou}, C. Nicopoulos, D. Hardy, B. Falsafi and Y. Sazeides\\[5pt]
\end{tabular}

\end{rSection}

\begin{rSection}{Awards and Accomplishments}

\begin{tabular}{L!{\VRule}R}
2013&\textbf{Powell Fellowship} for academic years 2013--2016, UCSD Computer Science and Engineering.\\[5pt]
2012&\textbf{HiPEAC Paper Award} for the paper titled ``NoCAlert: An on-line and real-time fault detection mechanism for network-on-chip architectures''.\\[5pt]
2011&\textbf{Best Senior Design Project Award} in the Department of Electrical and Computer Engineering, University of Cyprus for academic year 2010-2011.\\[5pt]
\end{tabular}

\end{rSection}

\nocite*
\bibliographystyle{plain}
\nobibliography{../publications}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
